EPE and Speed Adaptive Extended Kalman Filter for Vehicle Position and Attitude Estimation with Low Cost GNSS and IMU Sensors

### 2014-06-26 Paper/main.tex
Camera Ready Version

\begin{table}[ht]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Process Noise Standard Deviations}
\label{processnoisetable}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c l c}
\hline
Parameter & Decribtion & Value\\
\hline
$\sigma_a$ & Acceleration Process Noise & \SI{6.0}{\metre\per\square\second} \\
$\sigma_{\dot \psi}$ & Yawrate Process Noise & \SI{0.028}{\radian\per\second}\\
$\sigma_{\dot \phi}$ & Pitchrate Process Noise & \SI{0.070}{\radian\per\second}\\
$\sigma_{\dot \Theta}$ & Rollrate Process Noise & \SI{0.070}{\radian\per\second}\\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Process Noise Standard Deviations}
\label{processnoisetable}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c l l}
\hline
Parameter & Process Noise for & Value\\
\hline
$\sigma_a$ & Acceleration & \SI{6.0}{\metre\per\square\second} \\
$\sigma_{\dot \psi}$ & Yawrate & \SI{0.028}{\radian\per\second}\\
$\sigma_{\dot \phi}$ & Pitchrate & \SI{0.070}{\radian\per\second}\\
$\sigma_{\dot \Theta}$ & Rollrate & \SI{0.070}{\radian\per\second}\\
\hline
\end{tabular}
\end{table}
